Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-20 RR_manuscript/RR.Rmd
🚚 - rename Draft_RR to RR

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 1)

@@

no_analyses <- msa_models_unique %>%
  nrow()

@@

`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
Of the analysis submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after having seen all analytic strategies.

>>>>

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    left_join(select(teams, animal, leader = coordinator), by = "leader") %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(animal) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(animal) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(animal, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              median_size = median(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 1)

@@

no_analyses <- msa_models %>% 
  select(team, animal, model_n) %>% 
  distinct() %>% 
  nrow()

@@

`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
Of the analyses submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after having seen all analytic strategies.
